New lower bounds for Schur and weak Schur numbers

### 2021-04-09 article/schur.tex
Ajout intuition tableau

>>>>

The idea lying beneath this inequality is similar to Abbott and Hanson's
contruction. We build a table where every column is colored according
to a SF-template partition of order \(n+1\) and where there are
\(S^+(n)\) rows. The resulting coloring of the table gives a sum-free
partitions thnaks to the properties of the SF-template. We give the
following table for \(n = 2\) to make the intuition cleared. This
intuition will be formalised in the proof.
\begin{center}
\(\overset{S^+(3)}{S^+(2) \left \updownarrow\overleftrightarrow{\begin{tabular}{|*{7}{c|}}
	\hline
	\cellcolor{red} 1 & \cellcolor{blue} 2 & \cellcolor{blue} 3 & \cellcolor{green} 4 & \cellcolor{red} 5 & \cellcolor{green} 6 & \cellcolor{blue} 7 \\
	\hline
	\cellcolor{red} 8 & \cellcolor{blue} 9 & \cellcolor{blue} 10 & \cellcolor{green} 11 & \cellcolor{red} 12 & \cellcolor{green} 13 & \cellcolor{blue} 14\\
	\hline
	\cellcolor{red} 15 & \cellcolor{blue} 16 & \cellcolor{blue} 17 & \cellcolor{green} 18 & \cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{blue} 21 \\
	\hline
	\cellcolor{red} 22 & \cellcolor{blue} 23 & \cellcolor{blue} 24 & \cellcolor{green} 25 & \cellcolor{red} 26 & \cellcolor{green} 27 & \cellcolor{blue} 28 \\
	\hline
\end{tabular}}
\right.}\)
\end{center}
